\bf Effects of Word Alignment Visualization on Post-Editing Quality \& Speed

### 2015-09-07 paper/figure3.tex
Camera-ready for MT Summit

%%\addplot coordinates {(tool8,1) (tool9,1) (tool10,1)};
\legend{Monolingual PE with Alignments, PE with Alignments,PE no Alignments}
\end{axis}
\end{tikzpicture}
\caption{Russian-English}
\label{fig:mean_adequacy_score_per_posteditor_ru}
\end{center}
\end{subfigure}
\ \\ \ \\
\begin{subfigure}[b]{\linewidth}
\begin{center}
\begin{tikzpicture}[trim left={(-0.5,0)},trim axis right]
\begin{axis}[%scale only axis=true, width=60mm, height=73mm,
    ybar,
    enlargelimits=0.15,
    legend style={at={(0.5,1.05)},anchor=south},
%   ylabel={Mean Adequacy Score by Participant},
   xlabel={Post-Editor},
   % symbolic x coords={PE0,PE1,PE2,PE3,PE4,PE5,PE6},
    xtick={1,2,3,4},
    xticklabels={PE7,PE8,PE9,PE10},
	xtick pos=left,
	ytick pos=left,
	ylabel shift={-0.15cm},
	ymin=6,
	ymax=10,
    %xtick=data,
    %nodes near coords,
    %nodes near coords align={vertical},
    bar width=5pt
    ]

\addplot coordinates {};
\addplot coordinates {(1,8.8) (2,8.461538461538462) (3,8.56) (4,8.76923076923077) };
\addplot coordinates {(1,8.23076923076923) (2,8.72) (3,8.461538461538462) (4,8.88) };
\addplot[red,sharp plot,update limits=false] coordinates { (-1,7.686274509803922) (12,7.686274509803922) };

%%\addplot coordinates {(tool8,1) (tool9,1) (tool10,1)};
\legend{PE with Alignments,PE no Alignments}
\end{axis}
\end{tikzpicture}
\end{center}
\caption{Spanish-English}
\label{fig:mean_adequacy_score_per_posteditor_es}
\end{subfigure}
\caption{Mean adequacy score per post-editor. The red horizontal line indicates the mean adequacy score (Russian-English: 6.1; Spanish-English: 7.7) of the unedited MT.}
\label{fig:mean_adequacy_score_per_posteditor}
\end{figure}

>>>>

%%\addplot coordinates {(tool8,1) (tool9,1) (tool10,1)};
\legend{Monolingual PE with Alignments, PE with Alignments,PE no Alignments}
\end{axis}
\end{tikzpicture}
\caption{Russian-English}
\label{fig:mean_adequacy_score_per_posteditor_ru}
\end{center}
\end{subfigure}
\ \\ \ \\
\begin{subfigure}[b]{\linewidth}
\begin{center}
\begin{tikzpicture}[trim left={(-0.5,0)},trim axis right]
\begin{axis}[scale only axis=true, width=120mm, height=60mm,
    ybar,
    enlargelimits=0.15,
    legend style={at={(0.5,1.05)},anchor=south},
%   ylabel={Mean Adequacy Score by Participant},
   xlabel={Post-Editor},
   % symbolic x coords={PE0,PE1,PE2,PE3,PE4,PE5,PE6},
    xtick={1,2,3,4,5,6,7,8,9,10},
    xticklabels={PE7,PE8,PE9,PE10,PE11,PE12,PE13,PE14,PE15,PE16},
	xtick pos=left,
	ytick pos=left,
	ylabel shift={-0.15cm},
	ymin=6,
	ymax=10,
    %xtick=data,
    %nodes near coords,
    %nodes near coords align={vertical},
    bar width=5pt
    ]

%	Adequacy with align	Adequacy w/o align
%PE7	8.48	8.54
%PE8	8.46	8.16
%PE9	8.1	8.31
%PE10	8.46	8
%PE11	9.12	8.23
%PE12	8.15	7.44
%PE13	7.68	8.15
%PE14	8.23	7.76
%PE15	7.36	7.54
%PE16	8.23	8
%		
%Note overall mean for MT is 7.14

\addplot coordinates {};
\addplot coordinates {(1,8.48) (2,8.46) (3,8.1) (4,8.46) (5,9.12) (6,8.15) (7,7.68) (8,8.23) (9,7.36) (10,8.23) };
\addplot coordinates {(1,8.54) (2,8.16) (3,8.31) (4,8) (5,8.23) (6,7.44) (7,8.15) (8,7.76) (9,7.54) (10,8) };
%\addplot coordinates {(1,8.8) (2,8.461538461538462) (3,8.56) (4,8.76923076923077) };
%\addplot coordinates {(1,8.23076923076923) (2,8.72) (3,8.461538461538462) (4,8.88) };
\addplot[red,sharp plot,update limits=false] coordinates { (-1,7.14) (12,7.14) };

%%\addplot coordinates {(tool8,1) (tool9,1) (tool10,1)};
\legend{PE with Alignments,PE no Alignments}
\end{axis}
\end{tikzpicture}
\end{center}
\caption{Spanish-English}
\label{fig:mean_adequacy_score_per_posteditor_es}
\end{subfigure}
\caption{Mean adequacy score per post-editor. The red horizontal line indicates the mean adequacy score (Russian-English: 6.1; Spanish-English: 7.1) of the unedited MT.}
\label{fig:mean_adequacy_score_per_posteditor}
\end{figure}

### 2015-09-07 paper/figure7.tex
Camera-ready for MT Summit

\begin{figure}
\begin{subfigure}[b]{\linewidth}
\begin{center}
\begin{tikzpicture}[trim left={(-0.5,0)},trim axis right]
\begin{axis}[%scale only axis=true, width=80mm, height=73mm,
    ybar,
    enlargelimits=0.15,
    legend style={at={(0.5,1.05)},anchor=south},
   ylabel={Mean Adequacy Score by Participant},
   xlabel={Post-Editor},
   % symbolic x coords={PE0,PE1,PE2,PE3,PE4,PE5,PE6},
    xtick={0,1,2,3,4,5,6},
    xticklabels={PE0,PE1,PE2,PE3,PE4,PE5,PE6},
	xtick pos=left,
	ytick pos=left,
	ylabel shift={-0.15cm},
    %xtick=data,
    %nodes near coords,
    %nodes near coords align={vertical},
    bar width=5pt
    ]

\addplot coordinates { (0,7.0) (0,6.1)};
\addplot coordinates { (1,8.0) (2,9.8) (3,9.0) (4,8.2) (5,7.4) (6,7.7)};
\addplot coordinates { (1,7.6) (2,9.3) (3,8.8) (4,7.6) (5,6.7) (6,7.1)};

\addplot[red,sharp plot,update limits=false] 
	coordinates {(-1,6.1) (8,6.1)};
	%node[above] at (axis cs:3,6.1) {Unedited MT};

%%\addplot coordinates {(tool8,1) (tool9,1) (tool10,1)};
\legend{Monolingual PE with Alignments, PE with Alignments,PE no Alignments}
\end{axis}
\end{tikzpicture}
\caption{Russian-English}
\label{fig:mean_adequacy_score_per_posteditor_ru}
\end{center}
\end{subfigure}
\ \\ \ \\
\begin{subfigure}[b]{\linewidth}
\begin{center}
\begin{tikzpicture}[trim left={(-0.5,0)},trim axis right]
\begin{axis}[scale only axis=true, width=120mm, height=60mm,
    ybar,
    enlargelimits=0.15,
    legend style={at={(0.5,1.05)},anchor=south},
%   ylabel={Mean Adequacy Score by Participant},
   xlabel={Post-Editor},
   % symbolic x coords={PE0,PE1,PE2,PE3,PE4,PE5,PE6},
    xtick={1,2,3,4,5,6,7,8,9,10},
    xticklabels={PE7,PE8,PE9,PE10,PE11,PE12,PE13,PE14,PE15,PE16},
	xtick pos=left,
	ytick pos=left,
	ylabel shift={-0.15cm},
	ymin=6,
	ymax=10,
    %xtick=data,
    %nodes near coords,
    %nodes near coords align={vertical},
    bar width=5pt
    ]

%	Adequacy with align	Adequacy w/o align
%PE7	8.48	8.54
%PE8	8.46	8.16
%PE9	8.1	8.31
%PE10	8.46	8
%PE11	9.12	8.23
%PE12	8.15	7.44
%PE13	7.68	8.15
%PE14	8.23	7.76
%PE15	7.36	7.54
%PE16	8.23	8
%		
%Note overall mean for MT is 7.14

\addplot coordinates {};
\addplot coordinates {(1,8.48) (2,8.46) (3,8.1) (4,8.46) (5,9.12) (6,8.15) (7,7.68) (8,8.23) (9,7.36) (10,8.23) };
\addplot coordinates {(1,8.54) (2,8.16) (3,8.31) (4,8) (5,8.23) (6,7.44) (7,8.15) (8,7.76) (9,7.54) (10,8) };
%\addplot coordinates {(1,8.8) (2,8.461538461538462) (3,8.56) (4,8.76923076923077) };
%\addplot coordinates {(1,8.23076923076923) (2,8.72) (3,8.461538461538462) (4,8.88) };
\addplot[red,sharp plot,update limits=false] coordinates { (-1,7.14) (12,7.14) };

%%\addplot coordinates {(tool8,1) (tool9,1) (tool10,1)};
\legend{PE with Alignments,PE no Alignments}
\end{axis}
\end{tikzpicture}
\end{center}
\caption{Spanish-English}
\label{fig:mean_adequacy_score_per_posteditor_es}
\end{subfigure}
\caption{Mean adequacy score per post-editor. The red horizontal line indicates the mean adequacy score (Russian-English: 6.1; Spanish-English: 7.1) of the unedited MT.}
\label{fig:mean_adequacy_score_per_posteditor}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\begin{tikzpicture}[trim left={(-0.5,0)},trim axis right]
\begin{axis}[scale only axis=true, width=40mm, height=10mm,
    ybar,
    enlargelimits=0.15,
    legend style={at={(0.5,1.05)},anchor=south},
   ylabel={GER},
   %xlabel={Post-Editor},
   % symbolic x coords={PE0,PE1,PE2,PE3,PE4,PE5,PE6},
    xtick={0},
    ytick={1.47,2.53},
    xticklabels={""},
	xtick pos=left,
	ytick pos=left,
	ylabel shift={-0.15cm},
    %xtick=data,
    %nodes near coords,
    %nodes near coords align={vertical},
    bar width=20pt
    ]

\addplot 
	coordinates {};
\addplot coordinates { (1,2.53)};
\addplot coordinates { (1,1.47)};

%\addplot[red,sharp plot,update limits=false] 
%	coordinates {(-1,6.1) (8,6.1)};
	%node[above] at (axis cs:3,6.1) {Unedited MT};

%%\addplot coordinates {(tool8,1) (tool9,1) (tool10,1)};
\legend{PE with Alignments,PE no Alignments}
\end{axis}
\end{tikzpicture}
\caption{Mean adequacy gain to effort ratio (GER) values for segments post-edited with alignment and without alignment. Effort is measured by pause to word ratio (PWR).}
\label{fig:mean_ger}
\end{center}
\end{figure}

### 2015-09-07 paper/paper_abstract.tex
Camera-ready for MT Summit

\begin{abstract}
%
Phrase-based machine translation can be configured to produce alignment data that indicates which machine translated target language words correspond to which original source language words.
%
In most prior work that examined the efficacy of post-editing machine translation, post-editors were presented with machine translations (and in most cases the original source language sentences) without also being presented with source-to-target alignment links.
%
We select four news articles, and ask six Russian-English bilinguals and four Spanish-English bilinguals to post-edit English machine translation results, in some cases using alignments and in other cases without.
%
We obtain human adequacy judgements of the post-edited sentences, 
%
%and demonstrate
%along with human adequacy judgements for the unedited machine translations and the monolingual post-edited translations of \citet{2014_WMT_Schwartz_etal}.
%
%In this work, we 
and demonstrate that when machine translation quality is low, post-editing quality is consistently higher, by a statistically significant amount, when bilingual post-editors are presented with alignment data.
%
%We also find that monolingual post-edited translations are 
%
%In this work, we confirm prior work indicating that bilingual 
%
%As part of the Workshop on Statistical Machine Translation, \citet{2014_WMT_Schwartz_etal} examined the extent to which monolingual native English speakers were able to post-edit machine translation of news articles into fluent, adequate English translations of Russian source sentences.
%
\end{abstract}

>>>>

\begin{abstract}
%
Phrase-based machine translation can be configured to produce alignment data that indicates which machine translated target language words correspond to which original source language words.
%
In most prior work that examined the efficacy of post-editing machine translation, post-editors were presented with machine translations (and in most cases the original source language sentences) without also being presented with source-to-target alignment links.
%
We select four news articles, and ask six Russian-English bilinguals and eleven Spanish-English bilinguals to post-edit English machine translation results, in some cases using alignments and in other cases without.
%
We obtain human adequacy judgements of the post-edited sentences, 
%
%and demonstrate
%along with human adequacy judgements for the unedited machine translations and the monolingual post-edited translations of \citet{2014_WMT_Schwartz_etal}.
%
%In this work, we 
and demonstrate that when machine translation quality is low, post-editing quality is consistently higher, by a statistically significant amount, when bilingual post-editors are presented with alignment data.
%
%We also find that monolingual post-edited translations are 
%
%In this work, we confirm prior work indicating that bilingual 
%
%As part of the Workshop on Statistical Machine Translation, \citet{2014_WMT_Schwartz_etal} examined the extent to which monolingual native English speakers were able to post-edit machine translation of news articles into fluent, adequate English translations of Russian source sentences.
%
\end{abstract}

### 2015-09-07 paper/paper_intro.tex
Camera-ready for MT Summit

To address these questions, we conduct a bilingual post-editing experiment (\S\ref{sec:methodology}) where bilingual post-editors are presented with machine translation output of varying quality, with and without word-level alignment link visualization.
%
In the first condition, we ask six Russian-English bilingual translation students to post-edit two Russian language news articles starting with relatively low quality English machine translation.
%
In the second condition, we ask four Spanish-English bilingual translation students to post-edit two Spanish language news articles starting with relatively high quality English machine translation.
%
We find (\S\ref{sec:results}) that when machine translation quality is low, post-editing quality is consistently higher, by a statistically significant amount, when bilingual post-editors are presented with alignment data.
%
We find no statistically significant effect when machine translation quality is high.
%
We also found that for both Russian-English and Spanish-English the mean post-editing times were shorter for texts with alignment than for texts without alignment. These differences were not significant, but the difference for the Russian-English texts approached significance. 
%
Finally, in \S\ref{sec:background} we briefly survey the current state of post-editing research and situate this work within the context of related work in post-editing.

>>>>

To address these questions, we conduct a bilingual post-editing experiment (\S\ref{sec:methodology}) where bilingual post-editors are presented with machine translation output of varying quality, with and without word-level alignment link visualization.
%
In the first condition, we ask six Russian-English bilingual translation students to post-edit two Russian language news articles starting with relatively low quality English machine translation.
%
In the second condition, we ask eleven Spanish-English bilingual translation students to post-edit two Spanish language news articles starting with relatively high quality English machine translation.
%
We find (\S\ref{sec:results}) that when machine translation quality is low, post-editing quality is consistently higher, by a statistically significant amount, when bilingual post-editors are presented with alignment data.
%
We find no statistically significant effect when machine translation quality is high.
%
We also found that for both Russian-English and Spanish-English the mean post-editing times were shorter for texts with alignment than for texts without alignment. These differences were not significant, but the difference for the Russian-English texts approached significance. 
%
Finally, in \S\ref{sec:background} we briefly survey the current state of post-editing research and situate this work within the context of related work in post-editing.

### 2015-09-07 paper/paper_methodology.tex
Camera-ready for MT Summit

\subsubsection{Russian-English Bilingual Participants}
There were six participants who served as post-editors in the Russian-English portion of this study, all of whom were paid for their time.
%
These participants were all English-Russian bilinguals.
%
We designate these participants as PE1--PE6.
%
Four of the six bilingual participants (PE2, PE3, PE4, \& PE6) had Russian as their first language (L1) and were highly proficient in English as their second language (L2).
%
The other two bilingual participants (PE1 \& PE5) had English as their first language and were highly proficient in Russian as their second language.
%
Three of the six bilingual participants were graduate students and three were undergraduate students; all were enrolled in a university Russian Translation program. %and three were undergraduate students in the same program.
%a Russian Translation program at the same American university.

@@

There were eleven participants who served as post-editors in the Spanish-English portion of this study, all of whom were paid for their time. 
%
They were all Spanish-English bilinguals.
%
We designate these participants as PE7--PE17. 
%
The first language (L1) of all eleven participants was English, and all eleven were highly proficient in Spanish as their second language (L2). 
%
These participants were students in a university Master of Spanish Translation program.

@@

Each participant was instructed to edit one of the two texts using the interface where alignment links were shown,
%
and to edit the other text using the interface where alignment links were omitted.
%
Participants post-edited the two texts in one session lasting less than two hours, although there were no time limits set for the task.
%
Post-Editors 2, 4, and 6 were assigned to post-edit Doc A using the variant 1 interface that displayed alignments, and Doc B using the variant 2 interface that omitted alignments.
%
Post-Editors 1, 3, and 5 were assigned Doc A using variant 2 and Doc B using variant 1.

@@

Participants post-edited one text using the interface where alignment links were shown and the other text using the interface where alignment links were omitted. 
%
Participants post-edited the two texts in one session lasting less than one hour. 
%
Post-editors 7, 9, 11, 13, 15, and 17 edited Doc C using the interface that omitted the alignments and Doc D using the interface that displayed the alignments. 
%
Post-editors 8, 10, 12, 14, and 16 edited Doc C using the interface that displayed the alignments and Doc D using the interface that omitted the alignments.

>>>>

\subsubsection{Russian-English Bilingual Participants}
There were six participants who served as post-editors in the Russian-English portion of this study, all of whom were paid for their time at the rate of \$25 for each hour or part of an hour.
%
These participants were all English-Russian bilinguals.
%
We designate these participants as PE1--PE6.
%
Four of the six bilingual participants (PE2, PE3, PE4, \& PE6) had Russian as their first language (L1) and were highly proficient in English as their second language (L2).
%
The other two bilingual participants (PE1 \& PE5) had English as their first language and were highly proficient in Russian as their second language.
%
Three of the six bilingual participants were graduate students and three were undergraduate students; all were enrolled in a university Russian Translation program. %and three were undergraduate students in the same program.
%a Russian Translation program at the same American university.

@@

There were eleven participants who served as post-editors in the Spanish-English portion of this study, all of whom were paid for their time at the rate of \$25 for each hour or part of an hour. 
%
They were all Spanish-English bilinguals.
%
We designate these participants as PE7--PE17. 
%
The first language (L1) of all eleven participants was English, and all eleven were highly proficient in Spanish as their second language (L2). 
%
These participants were students in a university Master of Spanish Translation program.

@@

Each participant was instructed to edit one of the two texts using the interface where alignment links were shown,
%
and to edit the other text using the interface where alignment links were omitted.
%
Participants post-edited the two texts in one session lasting less than two hours, although there were no time limits set for the task.
%
The experimenter was present in the room and manually recorded the times taken.
%
Post-Editors 2, 4, and 6 were assigned to post-edit Doc A using the variant 1 interface that displayed alignments, and Doc B using the variant 2 interface that omitted alignments.
%
Post-Editors 1, 3, and 5 were assigned Doc A using variant 2 and Doc B using variant 1.

@@

Participants post-edited one text using the interface where alignment links were shown and the other text using the interface where alignment links were omitted. 
%
Participants post-edited the two texts in one session lasting less than one hour. 
%
Timings were recorded by a keylogger.
%
Post-editors 7, 9, 11, 13, 15, and 17 edited Doc C using the interface that omitted the alignments and Doc D using the interface that displayed the alignments. 
%
Post-editors 8, 10, 12, 14, and 16 edited Doc C using the interface that displayed the alignments and Doc D using the interface that omitted the alignments.

### 2015-09-07 paper/paper_results.tex
Camera-ready for MT Summit

\section{Results}
\label{sec:results}

\subsection{Rating Translation Adequacy}

@@

The times taken by the Russian-English post-editors to post-edit each text were recorded manually to the nearest minute. The mean times were 33 minutes for texts with alignment and 40 minutes for texts without alignment. This difference approached significance (p = .082).

@@

The times taken by the Spanish-English post-editors to post-edit each text were recorded by the keylogger to nearest millisecond. The mean times were 21 minutes  and 5 seconds for texts with alignment and 22 minutes and 5 seconds for texts without alignment. An independent samples t-test showed that these times are not significantly different from each other (t(18) = .295, p = .77.) 
%
Participants were not given time limitations, so timing data must be interpreted with caution. Note, however, that the mean time with alignment is numerically shorter than the mean time without alignment.

The shorter editing times for Spanish-English may in part be explained by the shorter length of these documents.

@@

The keystroke logging data gathered for Spanish-English post-editors allowed the computation of Pause to Word Ratio (PWR). For each segment, PWR is the ratio of the number of pauses exceeding 300ms to the number of words in the MT segment; it is a measure of cognitive effort in post-editing (Lacruz & Shreve, 2012). Higher PWR corresponds to higher cognitive effort.
% INSERT REF TO FIG 6 AND INSERT FIG 6
Contrary to expectation, the mean PWR for Spanish-English post-editors was slightly higher for the segments with alignment (0.70) than for those without alignment (0.63). However, the numerical difference was not significant.

@@

GER for segments with alignment was 2.53, and GER for segments without alignment was 1.47. Our prediction was confirmed: a paired samples t-test showed that GER was higher for segments with alignment (t(9) = 2.49, p =.034.)
%INSERT REF TO FIG 7 AND INSERT FIG 7

This result suggests that GER may be a robust metric for measuring the effects of alignment on post-editing. It would be interesting to conduct further studies involving language pairs different from Spanish-English where the adequacy of machine translations may be lower.

>>>>

\vspace{-2mm}
\section{Results}
\label{sec:results}

\vspace{-2mm}
\subsection{Rating Translation Adequacy}

@@

The times taken by the Russian-English post-editors to post-edit each text were recorded manually to the nearest minute.
%
Participants post-edited each text without a break.
%
They took a break of approximately five minutes between texts.
%
The mean times were 33 minutes for texts with alignment and 40 minutes for texts without alignment.
%
This difference approached significance (p = .082).

@@

The times taken by the Spanish-English post-editors to post-edit each text were recorded by the keylogger to nearest millisecond.
%
Participants post-edited each text without a break.
%
They took a break of approximately five minutes between texts.
%
The mean times were 21 minutes  and 5 seconds for texts with alignment and 22 minutes and 5 seconds for texts without alignment.
%
An independent samples t-test showed that these times are not significantly different from each other (t(18) = .295, p = .77.) 
%
Participants were not given time limitations, so timing data must be interpreted with caution. Note, however, that the mean time with alignment is numerically shorter than the mean time without alignment.
%
The shorter editing times for Spanish-English may in part be explained by the shorter length of these documents.

@@

\input{figure7}

The keystroke logging data gathered for Spanish-English post-editors allowed the computation of Pause to Word Ratio (PWR). For each segment, PWR is the ratio of the number of pauses exceeding 300ms to the number of words in the MT segment; it is a measure of cognitive effort in post-editing \citep{2014_Lacruz_Shreve}. Higher PWR corresponds to higher cognitive effort.
%
% Figure \Vref{fig:mean_pwr}
%
Contrary to expectation, the mean PWR for Spanish-English post-editors was slightly higher for the segments with alignment (0.70) than for those without alignment (0.63). However, the numerical difference was not significant.

@@

Figure \Vref{fig:mean_ger} \vpageref[above]{fig:mean_ger} shows GER for Spanish-English.
%
GER for segments with alignment was 2.53, and GER for segments without alignment was 1.47. Our prediction was confirmed: a paired samples t-test showed that GER was higher for segments with alignment (t(9) = 2.49, p =.034.).
%
%
%INSERT REF TO FIG 7 AND INSERT FIG 7
%
This result suggests that GER may be a robust metric for measuring the effects of alignment on post-editing. It would be interesting to conduct further studies involving language pairs different from Spanish-English where the adequacy of machine translations may be lower.

### 2015-09-07 paper/paper_title.tex
Camera-ready for MT Summit

\title{The Effect of Word Alignments in Bilingual and Monolingual Post-Editing}

\author{%
        {}\\
	    {}\\
	    {}\\
	    {}\\
	    {\tt}
}

\date{}

>>>>

%\title{Effects of Word Alignment Visualization on Post-Editing Quality \& Speed}
%
%\author{{}\\
%	    {}\\
%	    {}\\
%	    {}\\
%	    {\tt}
%}
%
%\date{}

\title{\bf Effects of Word Alignment Visualization on Post-Editing Quality \& Speed}

\author{\name{\bf Lane Schwartz} \hfill  \addr{lanes@illinois.edu}\\ 
        \addr{Dept. of Linguistics, University of Illinois at Urbana-Champaign, Urbana, IL 61801, USA}
\AND
        \name{\bf Isabel Lacruz} \hfill \addr{ilacruz@kent.edu}\\ 
       \name{\bf Tatyana Bystrova} \hfill \addr{tbystro2@kent.edu}\\
        \addr{Dept. of Modern \& Classical Language Studies, Kent State University, Kent, OH 44242, USA}
}
